\bf\mftitle

### 2011-01-20 doc/jInfer/architecture/architecture.tex
Documentation: finishing Architecture.

jInfer and its documentation uses extended context-free grammars\cite{extendedcfg}.
% TODO vektor check citation of http://www.engr.mun.ca/~theo/Courses/fm/pub/context-free.pdf in literature.bib
\emph{Rules} in such grammar are in the form
$$
  \textnormal{Left Hand Side (LHS)} \to \textnormal{Right Hand Side (RHS)}
$$
where LHS is a letter of the alphabet (token), RHS is a regular expression over this alphabet. Example would be
$$
  a \to b, (c | d)\ast
$$
In jInfer each such rule is represented with an \code{Element} instance. In this representation, the \code{Element} itself is the LHS, its \code{subnodes} are the RHS.\\

Another important notion is a \emph{grammar}. A grammar consists of its rules, so in jInfer a grammar is just a collection of \code{Element}s. Closely related term is \emph{Initial Grammar}, which for us is a grammar consisting of rules with \emph{simple} right hand sides, i.e. just concatenations of tokens (even with no children, see fig. \ref{xml_example} again). Initial Grammar is produced by \jmodule{Initial Grammar Generator}. % TODO vektor Link

@@

\subsection{Node metadata} \label{section_metadata} % TODO vektor Move after Programmatic view
To allow simple extensibility of rules, class \code{AbstractNamedNode} contains a string-addressed map called \code{metadata} that can contain arbitrary object values.\\

@@

TODO vektor

>>>>

jInfer and its documentation uses extended context-free grammars\cite{extendedcfg}.
% TODO vektor check citation of http://www.engr.mun.ca/~theo/Courses/fm/pub/context-free.pdf in literature.bib
% TODO anti what do you mean, "check citation"?
\emph{Rules} in such grammar are in the form
$$
  \textnormal{Left Hand Side (LHS)} \to \textnormal{Right Hand Side (RHS)}
$$
where LHS is a letter of the alphabet (token), RHS is a regular expression over this alphabet. Example would be
$$
  a \to b, (c | d)\ast
$$
In jInfer each such rule is represented with an \code{Element} instance. In this representation, the \code{Element} itself is the LHS, its \code{subnodes} are the RHS.\\

Another important notion is a \emph{grammar}. A grammar consists of its rules, so in jInfer a grammar is just a collection of \code{Element}s. Closely related term is \emph{Initial Grammar}, which for us is a grammar consisting of rules with \emph{simple} right hand sides, i.e. just concatenations of tokens (even with no children, see fig. \ref{xml_example} again). Initial Grammar is produced by \jmodule{Initial Grammar Generator}.

@@

\subsection{Node metadata} \label{section_metadata}
To allow simple extensibility of rules, class \code{AbstractNamedNode} contains a string-addressed map called \code{metadata} that can contain arbitrary object values.\\

@@

An important topic related to NB modules and their dependencies is a notion of \emph{tokens}. Imagine a situation where module \emph{M} needs \emph{someone} else to provide a certain service \emph{S}, but doesn't care who will that be. It cannot declare a direct dependency on a module containing this service provider, because it might not know such a module. Instead, \emph{M} declares a \emph{required token}. Any module providing \emph{S} will declare a \emph{provided token}, which is a simple string (usually fully qualified Java name of the interface representing \emph{S}). Later, NBP will make sure that \emph{M} can be installed in the platform only if there is at least one module providing that specific token.\\

jInfer uses tokens in the following way: \jmodule{Runner}, as the module encapsulating the inference process, and \jmodule{ProjectType} as an encapsulation of jInfer projects both require the following 3 tokens.

\begin{itemize}
	\item \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference.IGGenerator}
	\item \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference.SchemaGenerator}
	\item \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference.Simplifier}
\end{itemize}

All inference modules declare their respective token as provided. This way it is ensured that jInfer will run only if there is at least one implementation of each of the inference modules, regardless of the implementation itself.
